A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-02 mt-marathon.2013/PBML_article.tex
Add plots
more

\subsection{CDEC}
CDEC eschew the dense and sparse hybrid approach and implement only sparse maps. Dense features can still be modelled in the framework with sparse features, with some loss of efficiency.

@@

\subsection{Joshua}
As with CDEC, Joshua only supports sparse features, however, it uses a different strategy to improve efficiency.

@@

>>>>

\subsection{cdec}
cdec eschew the dense and sparse hybrid approach and implement only sparse maps. Dense features can still be modelled in the framework with sparse features, with some loss of efficiency.

@@

\subsection{Joshua}
As with cdec, Joshua only supports sparse features, however, it uses a different strategy to improve efficiency.

@@

\section{Results}

Given the same formalism and
